An Evaluation of Methods for Assessing Model Fit for Bayesian Diagnostic Classification Models

### 2024-06-13 manuscript/manuscript.qmd
finish discussion

The simulation and subsequent analyses were conducted in R version `r getRversion()` [@R-base].
All DCMs were estimated using *Stan* [version `r rstan::stan_version()`, @stan] via the measr package [@thompson-joss-2023; @R-measr], and replications were conducted on AWS EC2 instances using the portableParallelSeeds package [@R-portableParallelSeeds].
All R code for the simulation and subsequent analyses is available in a public OSF project repository.^[https://osf.io/t5v96/]

@@

There are some limitations to the present study.
For example, we only investigated

@@

Model fit is a crucial evaluation of model performance for any psychometric model, including DCMs.
The present study demonstrates the greater utility of absolute and relative fit indices that can be used with a Bayesian estimation procedure for DCMs.

>>>>

The simulation and subsequent analyses were conducted in R version `r getRversion()` [@R-base].
All DCMs were estimated using *Stan* [version `r rstan::stan_version()`, @stan] via the measr package [@thompson-joss-2023; @R-measr], and replications were conducted on AWS EC2 instances using the portableParallelSeeds package [@R-portableParallelSeeds].
All R code for the simulation and subsequent analyses is available in a public OSF project repository.^[<https://osf.io/t5v96/>]

@@

There are some limitations to the present study.
For example, we investigated a relatively limited set of test designs.
Future research should confirm the efficacy of the PPMC &chi;^2^ and LOO under more complex designs (e.g., more attributes, more complex item structures).
Additionally, the present study assumed that a DCM was always desired, and therefore model comparisons focused on choosing between different DCM subtypes.
Future research could also consider how the LOO behaves when choosing between different psychometric models.
For example, we may compare a Bayesian DCM to an item response theory model also estimated with a Bayesian procedure.

@@

Model fit is a crucial evaluation of model performance for any psychometric model, including DCMs.
It is important not just to evaluate model fit, but also to ensure that we are using the best methods possible for the evaluation.
The present study offers evidence that the PPMC &chi;^2^ and LOO, which can only be utilized with a Bayesian estimation is used, offer improvements over existing maximum likelihood measures of model fit.
By using improved methods for model evaluation, we can greater confidence that the inferences of student proficiency we draw from DCMs are valid indicates of the students' knowledge and skills.
